\subsection{Balls detection}
To detect balls, Michele proposed a multi-step preprocessing approach. Initially, the table region is isolated using an approach similar to the segmentation described before. Then the corner-defined area is removed to prevent the Hough Circle transform from finding them as false positives. Subsequently, k-means clustering was applied to the image with k=5 (the number of balls type plus the playing field). The resulting clustered \texttt{Mat} is converted to gray-scale to be used as \texttt{HoughCircles} input. The gray-scale output colors were selected to be as different as possible from each other once the color space is changed.

Circle parameters, such as radius and center color, are analyzed to identify potential ball regions. By calculating the mean radius of in-table circles with a center not selected by the color mask, a radius range is established. Circles within this radius range are then considered for further analysis.

Ball classification involves creating a circular mask, computing the gray-scale histogram, and excluding background pixels from the values of the histogram. Peak values in the histogram are used to differentiate between striped and solid balls, while HSV color space analysis is used to distinguish white and black balls.

After finding the balls, the team identified an optimization opportunity. Since in an 8-ball game, there must always be one and only one white ball and one and only one black ball, Michele implemented non-maxima suppression for white and black balls independently, in order to improve performance.

The result of the detection process is then used to segment the balls.
